---
title: "generate_data"
author: "Sara Orofino"
date: "3/12/2020"
output: html_document
---

```{r setup}
library(tidyverse)
library(here)
library(devtools)
```

##Generate Function Data


###extent
Want to include in the package some existing data from NOAA and the National Snow and Ice Data Center. These data references are also linked in the function documentation.    

Data from: ftp://sidads.colorado.edu/DATASETS/NOAA/G02135/north/monthly/data/  
Userguide: https://nsidc.org/data/G02135/versions/3  

Available on a monthly basis. I will include data for two months as sample data. Sea Ice extent in the Northern Hemisphere reaches a maximum in March and a minimum in September, so these are the two that I will include for example data.  
```{r extent-data}
#read in data from the downloaded data folder 
#using here() brings the directory to whereever you've locally cloned the climate repo
march_extent <- read_csv(file = file.path(here(), "/downloaded_data/N_03_extent_v3.0.csv"))
sept_extent <- read_csv(file = file.path(here(), "/downloaded_data/N_03_extent_v3.0.csv"))

#store the data to the package:
use_data(march_extent, pkg=climate, overwrite = TRUE)
use_data(sept_extent, pkg=climate, overwrite =  TRUE)
```

###si_extremes  
Also want to include in the package some monthly data on sea ice extents for multiple years. These data come from the same data source but I combined all of the months into a single data frame.    

```{r extremes-data}
#read in data from the downloaded data folder 
#using here() brings the directory to whereever you've locally cloned the climate repo
extent_data <- read_csv(file = file.path(here(), "/downloaded_data/N_seaice_extent_v3.0.csv"))

#store the data to the package:
use_data(extent_data, pkg=climate, overwrite=TRUE)
```

