---
title: "apply_climate"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Put the title of your vignette here}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

##Package Overview

This climate package contains functions to calculate different trends in sea ice extent and possible sea level rise equivalents of melting a given volume of sea ice.  


##Examples

###sle()

The sle function calculates sea level rise equivalent (mm) for melting any given volume (cubed kilometer) of sea ice  
For more information see help(sle)  

```{r sle-example}
library(climate)

sle(ice_vol = 500, above = 0.6)
```

###extent

The extent function is used to calculate the rate of change in sea ice extent between two years  
For more information see help(extent)  

```{r extent-example, message=FALSE, warning=FALSE}

data("march_extent")
data("sept_extent")

extent(year1 = 1995, year2 = 2010, ext = sept_extent, showplot = T)
```

###si_extremes

The si_extremes function is used to calculate the maximum and minimum sea ice extent and the corresponding year and month  
For more information see help(si_extremes)  

```{r si_extremes-example, message=FALSE}

data("extent_data")

si_extremes(si = extent_data, showtable = F)

```

